---
title: "Book of Mormon Sentiment Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: flatly
runtime: shiny
---

```{r setup, include=FALSE}

library(flexdashboard)
library(shiny)
library(tidyverse)
library(tidytext)
library(textdata)
library(rvest)
library(wordcloud)
library(ggthemes)

```

```{r}
# list of books 
books <- c("1 Nephi", "2 Nephi", "Jacob", "Enos", "Jarom", "Omni", "Words of Mormon", "Mosiah", "Alma", "Helaman", "3 Nephi", "4 Nephi", "Mormon", "Ether", "Moroni")

book_labels <- c("1 Nephi", "2 Nephi", "Jacob", "", " ", "  ", "    ", "Mosiah", "Alma", "Helaman", "3 Nephi", "      ", "Mormon", "Ether", "Moroni", "       ")

booklist <- tibble(books) %>% 
  mutate(
    num_chapters = as.vector(c(22, 33, 7, 1, 1, 1, 1, 29, 63, 16, 30, 1, 9, 15, 10)),
    book_code = as.character(c("1-ne", "2-ne", "jacob", "enos", "jarom", "omni", "w-of-m", "mosiah", "alma", "hel", "3-ne", "4-ne", "morm", "ether", "moro"))
  )

custom_stop_words <- tribble(
  ~word, ~lexicon,
  "ye", "CUSTOM",
  "pass", "CUSTOM",
  "yea", "CUSTOM",
  "thy", "CUSTOM",
  "behold", "CUSTOM",
  "wherefore", "CUSTOM",
  "thou", "CUSTOM",
  "hath", "CUSTOM",
  "beheld", "CUSTOM",
  "people", "CUSTOM"
)

```

```{r preprocessing}

## This code is commented out so that it doesn't reprocess it every time the dashboard loads

# # Loop thru book_codes and chapters to scrape data
# 
# for (i in seq(booklist$book_code)) {
#   # get book code
#   code <- booklist$book_code[i]
#   # filter by book code
#   x <- booklist %>% filter(book_code == code)
# 
#   for (j in seq(x$num_chapters)) {
#     # get chapters
#     chapters <- x$num_chapters[j]
#     # Web scrap
#     text <- read_html(paste0("https://www.churchofjesuschrist.org/study/scriptures/bofm/", code, "/", j, "?lang=eng")) %>%
#       html_nodes("#content") %>% # the part of the website you want, Selector Gadget to find out the node
#       html_text() %>%
#       str_split("(\\.|\\:)(\\d|\\d\\d)\\s") %>%
#       unlist()
#     # Tidy Text
#     y <- tibble(text) %>%
#       mutate(
#         book_code = code,
#         chapter = j,
#         verse = row_number()
#       ) %>%
#       unnest_tokens(word, text) %>%
#       anti_join(stop_words) %>%
#       anti_join(custom_stop_words)
#     # if first iteration
#     if(j == 1 & code == "1-ne") {
#       tidy_text <- y
#     }
#     # Combine the tibbles
#     tidy_text <- rbind(tidy_text, y)
#   }
# 
# }
# 
# # Write tidy_text to csv so that it doens't redo the webscrapping
# write_csv(tidy_text, "data/bom_tidy.csv")

# read in data
tidy_text <- read_csv(here::here("data", "bom_tidy.csv")) %>% 
  inner_join(booklist, by = "book_code") %>% 
  select(books, book_code, num_chapters, chapter, verse, word)

```

Sidebar {.sidebar}
=======================================================================

### Welcome

__Explore your favorite chapters of the Book of Mormon and see what words get used the most and the overall sentiment of books and chapters using the inputs below.__

******

### User Inputs

```{r}

selectInput(
  "bk",
  label = "Select Book",
  choices = unique(tidy_text$books),
  selected = "1 Nephi"
)

renderUI({
  selectInput(
    "chp",
    label = "Select Chapter",
    choices = c(
      1:max(tidy_text$num_chapters[tidy_text$books == input$bk])
    ),
    selected = 1
  )
})

sliderInput(
  "bktop",
  label = "Number of Top Words (book)",
  min = 5,
  max = 15,
  value = 10,
  step = 1,
  round = TRUE,
  ticks = FALSE
)

sliderInput(
  "chptop",
  label = "Number of Top Words (chapter)",
  min = 5,
  max = 15,
  value = 10,
  step = 1,
  round = TRUE,
  ticks = FALSE
)

```

_For visualization purposes only a range of 5-15 is used for selecting the top number of words._

******

All text data is scrapped from [The Church of Jesus Chirst of Latter-day Saints](https://www.churchofjesuschrist.org/study/scriptures/bofm?lang=eng)

Text Analysis
=======================================================================

Row
-----------------------------------------------------------------------

### Book Word Cloud

```{r book wordcloud}

# Make a word cloud as well for another visualization practice
set.seed(42)

# # the colors help show the more important words over the not as important ones
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   count(word) %>%
#   with(
#     wordcloud(
#       word,
#       n,
#       min.freq = 2,
#       max.words = 400,
#       random.order=FALSE,
#       rot.per=0.35,
#       scale=c(4,0.1),
#       colors = brewer.pal(8, "Dark2")
#     )
#   )

renderPlot({
  tidy_text %>% 
    filter(books == input$bk) %>%
    count(word) %>% 
    with(
      wordcloud(
        word,
        n, 
        min.freq = 2,
        max.words = 400,
        random.order=FALSE, 
        rot.per=0.35, 
        scale=c(3.5,0.25),
        colors = brewer.pal(8, "Dark2")
      )
    )
})


```

### Book Top Words

```{r book top words}
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   count(word) %>%
#   mutate(word = fct_reorder(word, n)) %>%
#   arrange(desc(n)) %>% 
#   head(10) %>% 
#   ggplot(aes(x = word, y = n)) +
#   geom_col() +
#   coord_flip()

renderPlot({
  tidy_text %>%
    filter(books == input$bk) %>%  
    count(word) %>%
    mutate(word = fct_reorder(word, n)) %>%
    arrange(desc(n)) %>% 
    head(input$bktop) %>% 
    ggplot(aes(x = word, y = n)) +
    geom_col(fill = "#1B9E77") + 
    coord_flip() +
    labs(
      title = paste("Top", input$bktop, "Words in", input$bk),
      y = "Occurances"
    ) +
    theme_tufte() +
    theme(
      axis.title.y = element_blank(),
      axis.ticks = element_blank()
    )
})
```

Row
-----------------------------------------------------------------------

### Chapter Word Cloud

```{r chapter wordcloud}

# Make a word cloud as well for another visualization practice
set.seed(42)

# # the colors help show the more important words over the not as important ones
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   count(word) %>%
#   with(
#     wordcloud(
#       word,
#       n,
#       min.freq = 2,
#       max.words = 200,
#       random.order=FALSE,
#       rot.per=0.35,
#       scale=c(3.5,0.25),
#       colors = brewer.pal(11, "RdYlBu")
#     )
#   )

renderPlot({
  tidy_text %>% 
    filter(books == input$bk) %>% 
    filter(chapter == input$chp) %>% 
    count(word) %>% 
    with(
      wordcloud(
        word,
        n, 
        min.freq = 2,
        max.words = 200,
        random.order=FALSE, 
        rot.per=0.35, 
        scale=c(4,0.1),
        colors = brewer.pal(8, "Dark2")
      )
    )
})


```

### Chapter Top Words

```{r chapter top words}
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   count(word) %>%
#   mutate(word = fct_reorder(word, n)) %>%
#   arrange(desc(n)) %>%
#   head(10) %>% 
#   ggplot(aes(x = word, y = n)) + 
#   geom_col(fill = "#1B9E77") +
#   coord_flip() +
#   labs(
#     title = paste("Top", "10", "Words in", "1 Nephi", "1"),
#     y = "Occurances"
#   ) +
#   theme_tufte() +
#   theme(
#     axis.title.y = element_blank(),
#     axis.ticks = element_blank()
#   )
    

renderPlot({
  tidy_text %>%
    filter(books == input$bk) %>% 
    filter(chapter == input$chp) %>% 
    count(word) %>%
    mutate(word = fct_reorder(word, n)) %>%
    arrange(desc(n)) %>% 
    head(input$chptop) %>% 
    ggplot(aes(x = word, y = n)) +
    geom_col(fill = "#1B9E77") + 
    coord_flip() +
    labs(
      title = paste("Top", input$chptop, "Words in", input$bk, input$chp),
      y = "Occurances"
    ) +
    theme_tufte() +
    theme(
      axis.title.y = element_blank(),
      axis.ticks = element_blank()
    )
})

```

Row
-----------------------------------------------------------------------

### Book of Mormon Word Cloud

```{r bom wordcloud}

# Make a word cloud as well for another visualization practice
set.seed(42)

# # the colors help show the more important words over the not as important ones
# tidy_text %>%
#   count(word) %>%
#   with(
#     wordcloud(
#       word,
#       n,
#       min.freq = 2,
#       max.words = 400,
#       random.order=FALSE,
#       rot.per=0.35,
#       scale=c(4,0.1),
#       colors = brewer.pal(8, "Dark2")
#     )
#   )

renderPlot({
  tidy_text %>% 
    count(word) %>% 
    with(
      wordcloud(
        word,
        n, 
        min.freq = 2,
        max.words = 400,
        random.order=FALSE, 
        rot.per=0.35, 
        scale=c(4,0.1),
        colors = brewer.pal(8, "Dark2")
      )
    )
})


```

### Total Book of Mormon

```{r bom top words}
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   count(word) %>%
#   mutate(word = fct_reorder(word, n)) %>%
#   arrange(desc(n)) %>% 
#   head(10) %>% 
#   ggplot(aes(x = word, y = n)) +
#   geom_col() +
#   coord_flip()

renderPlot({
  tidy_text %>%
    count(word) %>%
    mutate(word = fct_reorder(word, n)) %>%
    arrange(desc(n)) %>% 
    head(input$bktop) %>% 
    ggplot(aes(x = word, y = n)) +
    geom_col(fill = "#1B9E77") + 
    coord_flip() +
    labs(
      title = paste("Top", input$bktop, "Words in the Book of Mormon"),
      y = "Occurances"
    ) +
    theme_tufte() +
    theme(
      axis.title.y = element_blank(),
      axis.ticks = element_blank()
    )
})
```

Sentiment Analysis
=======================================================================

Row
----------------------------------------------------------------------

### Book Sentiment

```{r book sentiment}
# tidy_text %>% 
#   filter(book_code == "1-ne") %>% 
#   inner_join(get_sentiments("bing")) %>% 
#   count(chapter, sentiment) %>% 
#   pivot_wider(
#     names_from = sentiment,
#     values_from = n,
#     values_fill = list(n = 0)
#   ) %>% 
#   mutate(
#     sentiment = positive - negative,
#     sign = ifelse(sentiment >= 0, "positive", "negative")
#   ) %>% 
#   ggplot(aes(chapter, sentiment, fill = sign)) +
#   geom_col(position = "dodge") + 
#   scale_fill_manual(values=c("#A5771D","#1B9E77")) +
#   theme(
#     legend.position = "none"
#   )

renderPlot({
  tidy_text %>% 
    filter(books == input$bk) %>% 
    inner_join(get_sentiments("bing")) %>% 
    count(chapter, sentiment) %>% 
    pivot_wider(
      names_from = sentiment,
      values_from = n,
      values_fill = list(n = 0)
    ) %>% 
    mutate(
      sentiment = positive - negative,
      sign = ifelse(sentiment >= 0, "positive", "negative")
    ) %>% 
    ggplot(aes(chapter, sentiment, fill = sign)) +
    geom_col(position = "dodge") + 
    scale_fill_manual(values=c("#A5771D","#1B9E77"), name = "Sentiment") +
    labs(
      title = paste("Sentiment Score Through", input$bk, "Chapters"),
      y = "Sentiment Score",
      x = "Chapter"
    ) +
    theme_tufte() +
    theme(
      axis.ticks.y = element_blank(),
      text = element_text(family = "Helvetica Neue")
    )
})


```

Row
----------------------------------------------------------------------

### Chapter Sentiment

```{r chapter sentiment}
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   inner_join(get_sentiments("bing")) %>%
#   count(verse, sentiment) %>%
#   pivot_wider(
#     names_from = sentiment,
#     values_from = n,
#     values_fill = list(n = 0)
#   ) %>%
#   mutate(
#     sentiment = positive - negative,
#     sign = ifelse(sentiment >= 0, "positive", "negative")
#   ) %>%
#   ggplot(aes(verse, sentiment, fill = sign)) +
#   geom_col(position = "dodge") +
#   scale_fill_manual(values=c("#A5771D","#1B9E77"), name = "Sentiment") +
#   labs(
#     title = "Title",
#     y = "Sentiment Score",
#     x = "Verse"
#   ) +
#   theme_tufte() +
#   theme(
#     axis.ticks.y = element_blank()
#   )

renderPlot({
  tidy_text %>% 
    filter(books == input$bk) %>% 
    filter(chapter == input$chp) %>% 
    inner_join(get_sentiments("bing")) %>% 
    count(verse, sentiment) %>% 
    pivot_wider(
      names_from = sentiment,
      values_from = n,
      values_fill = list(n = 0)
    ) %>% 
    mutate(
      sentiment = positive - negative,
      sign = ifelse(sentiment >= 0, "positive", "negative")
    ) %>% 
    ggplot(aes(verse, sentiment, fill = sign)) +
    geom_col(position = "dodge") + 
    scale_fill_manual(values=c("#A5771D","#1B9E77"), name = "Sentiment") +
    labs(
      title = paste("Sentiment Score Through", input$bk, input$chp, "Verses"),
      y = "Sentiment Score",
      x = "Verse"
    ) +
    theme_tufte() +
    theme(
      axis.ticks.y = element_blank(),
      text = element_text(family = "Helvetica Neue")
    )
})

```

Row
----------------------------------------------------------------------

### Book of Mormon Sentiment

```{r bom sentiment}
# tidy_text %>%
#   filter(book_code == "1-ne") %>%
#   filter(chapter == 1) %>%
#   inner_join(get_sentiments("bing")) %>%
#   count(verse, sentiment) %>%
#   pivot_wider(
#     names_from = sentiment,
#     values_from = n,
#     values_fill = list(n = 0)
#   ) %>%
#   mutate(
#     sentiment = positive - negative,
#     sign = ifelse(sentiment >= 0, "positive", "negative")
#   ) %>%
#   ggplot(aes(verse, sentiment, fill = sign)) +
#   geom_col(position = "dodge") +
#   scale_fill_manual(values=c("#A5771D","#1B9E77"), name = "Sentiment") +
#   labs(
#     title = "Title",
#     y = "Sentiment Score",
#     x = "Verse"
#   ) +
#   theme_tufte() +
#   theme(
#     axis.ticks.y = element_blank()
#   )

renderPlot({
  tidy_text %>% 
    inner_join(get_sentiments("bing")) %>% 
    count(books, chapter, sentiment) %>% 
    pivot_wider(
      names_from = sentiment,
      values_from = n,
      values_fill = list(n = 0)
    ) %>% 
    mutate(
      sentiment = positive - negative,
      sign = ifelse(sentiment >= 0, "positive", "negative")
    ) %>%
    ggplot(aes(chapter, sentiment, fill = sign)) +
    geom_col(position = "dodge") + 
    scale_fill_manual(values=c("#A5771D","#1B9E77"), name = "Sentiment") +
    labs(
      title = paste("Sentiment Score Throughout the Book of Mormon Chapters"),
      y = "Sentiment Score",
      x = "Book"
    ) +
    theme_tufte() +
    theme(
      axis.ticks.y = element_blank(),
      text = element_text(family = "Helvetica Neue"),
      axis.ticks.x = element_blank(),
      axis.text.x =element_blank(), 
      axis.title.x = element_blank(),
      strip.text.x = element_text(angle = 90),
      legend.position = "none"
    ) +
  facet_grid(~factor(books, levels = book_labels, ordered = TRUE), scales = "free_x", space = "free_x", switch = "x", labeller=label_wrap_gen(width = 1000, multi_line = TRUE))
})

```

