---
title: "BYU Marketing Lab"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: cosmo
---

```{r packages, include=FALSE}

# Install gtrendsR
# install.packages("plotly")

# Packages
library(flexdashboard)
library(shiny)
library(gtrendsR)
library(tidyverse)
library(plotly)
library(ggplot2)
library(DT)
library(rsconnect)

# Package Required For Streamgraph installed from github repo
# devtools::install_github("hrbrmstr/streamgraph")
library(streamgraph)

# Packages Required For Topic Mapping
library(tidytext)
library(igraph)
library(ggraph)

# Import State Dataset We can use for long lists of states for choices in inputs
states <- read_csv(here::here("data","states_list.csv")) %>% 
  mutate(
    country = "US",
    state_code = str_c(country, Abbreviation, sep = "-")
  )

# US Population data from census bureau
uspop <- read.csv(here::here("data", "2019PopByRegionAndState.csv")) %>% 
  rename(location = "Region")

```

```{r reactive}
# By Region Reactive Element
by_region <- reactive({
  output_results_us <- gtrends(keyword = input$keyword1_id,
      geo = "US",  #default always US 
      time = input$time_id)
  
  # output_results %>% summary()
  
  by_region <- output_results_us %>%
    .$interest_by_region %>% group_by(location, keyword) %>% summarize(hits) %>% drop_na()
  
  by_region <- by_region %>% arrange(desc(hits)) %>% mutate( ToHighlight = ifelse( location == input$highlight_id, "yes", "no" ) )
})

# By region per Capita
by_region_pop <- reactive({
  by_region = by_region()

  by_region_pop <- inner_join(by_region, uspop, by = "location")
  by_region_pop$hitspercapita <- by_region_pop$hits/by_region_pop$Pop
  
  
  # Interest by region per capita
  by_region_pop <- by_region_pop %>%
    group_by(location, keyword) %>% summarize(hitspercapita) %>% drop_na()
  
  by_region_pop <- by_region_pop %>% arrange(desc(hitspercapita)) %>% mutate( ToHighlight = ifelse( location == input$highlight_id, "yes", "no" ) )
})

# Interest Over Time Reactive Element
int_over_time <- reactive({
  
   STATE <- gtrends(keyword = input$keyword1_id,
        geo = input$geo_id,  # other option include today 12-m, 
        time = input$time_id) %>% 
    .$interest_over_time

  # MO <- output_results_1 %>%
  #   .$interest_over_time 

  US <- gtrends(keyword = input$keyword1_id,
        geo = "US",  #default always US 
        time = input$time_id) %>% 
    .$interest_over_time

  # US <- output_results_2 %>%
  #   .$interest_over_time 
  
  int_over_time <- rbind(STATE,US)
  int_over_time %>% arrange(desc(date))
  int_over_time <- rename(int_over_time, Region ="geo")
  
})

# Top Queries Reactive Element
topqueries <- reactive({
  US <- gtrends(keyword = input$keyword1_id,
        geo = "US",  #default always US 
        time = input$time_id)

  US_related <- as_tibble(US$related_queries)

# output_results_2_related <- as_tibble(output_results_2$related_queries)


  # Get top queries
  topqueries <- US_related %>% 
    filter(related_queries == 'top') %>% 
    unnest_tokens(bigram, value, token = 'ngrams', n = 3) %>% 
    separate(bigram, c("word1", "word2", "word3"), sep = " ") %>% 
    filter(!word1 %in% stop_words$word, !word2 %in% stop_words$word, !word3 %in% stop_words$word) 
})

# Rising Queries Reactive Element
risingqueries <- reactive({
  US <- gtrends(keyword = input$keyword1_id,
        geo = "US",  #default always US 
        time = input$time_id)

  US_related <- as_tibble(US$related_queries)
  

  risingqueries <- US_related %>% 
    filter(related_queries == 'rising') %>% 
    unnest_tokens(bigram, value, token = 'ngrams', n = 3) %>% 
    separate(bigram, c("word1", "word2", "word3"), sep = " ") %>% 
    filter(!word1 %in% stop_words$word, !word2 %in% stop_words$word, !word3 %in% stop_words$word)
})

```

```{r practice}

# US <- gtrends(keyword = c("Sustainable", "Eco-friendly"),
#         geo = "US",  #default always US 
#         time = "all")
# 
#   US_related <- as_tibble(US$related_queries)
#   
#   
#   word_counts <- US_related %>% 
#     select(value) %>% 
#     unnest_tokens(word, value) %>% 
#     count(word, sort = TRUE) %>% 
#     filter(!word %in% stop_words$word)
# 
#   risingqueries_bigram <- US_related %>% 
#     filter(related_queries == 'rising') %>% 
#     unnest_tokens(bigram, value, token = 'ngrams', n = 3) %>% 
#     separate(bigram, c("word1", "word2", "word3"), sep = " ") %>% 
#     filter(!word1 %in% stop_words$word, !word2 %in% stop_words$word, !word3 %in% stop_words$word) %>%
#     count(word1, word2, sort = TRUE) %>% 
#     filter(!is.na(word1), !is.na(word2)) %>% 
#     graph_from_data_frame(vertices = word_counts) 
```

Inputs {.sidebar}
=====================================================================

Adjust the inputs below then press __Go__ to run analysis

```{r}
actionButton("goButton", "Go")
```

******

```{r inputs}

# Select Keyword
textInput(
  inputId = "keyword1_id",
  label = "Select Keyword",
  value = "Sustainable"
)

# add apply button so the graph doesn't refresh automatically
# applyButton()

# highlighted state input
selectInput(
  inputId = "highlight_id",
  label = "Select State to Highlight",
  choices = unique(states[,1]),
  selected = "Missouri"
)

# Select Time
selectInput(
  inputId = "time_id",
  label = "Select Time",
  choices = c("now 1-H", "now 4-H", "now 1-H", "now 1-d", "now 7-d", "today 1-m", "today 12-m", "today+5-y", "all"),
  selected = "all"
)

# Select Geo Region
selectInput(
  inputId = "geo_id",
  label = "Select Geographical Region",
  # choices = c("US-MO","US"),
  choices = c(unique(states[,5]), "US"),
  selected = "US-MO"
)

```

_Geographical Region is for the interest over time and query related charts_

******

__NOTE__: The Go button is still being worked on for all the charts

Google Trends
=====================================================================

Hits By Region
-----------------------------------------------------------------------

### Hits By Region

```{r}

by_regionplot <- eventReactive(input$goButton, {
  
  # by_regionplot <- reactiveValues()

   by_region = by_region()

  # filter data for top 25 locations
  top_25 <- by_region %>%
    filter(hits >= 3) %>%
    head(25)

  # select the highlighted location
  highlight <- by_region %>%
    # filter(hits >= 3) %>%
    filter(ToHighlight == "yes")

  # For loop to
  if(any(top_25$ToHighlight == "yes") == TRUE) {
    region <- top_25
  } else{
    region <- rbind(top_25, highlight)
  }

  by_regionplot <- region %>%
    ggplot(aes(x = reorder(location, hits), y = hits, fill = ToHighlight )) +
    geom_col() +
    coord_flip() +
    labs(title = paste("Hits by Region for Search Term:", input$keyword1_id),
         x = "Location",
         y = "Number of Hits") +
    scale_fill_manual( values = c( "yes"="#007dc2", "no"="gray" ), guide = FALSE ) +
    theme_minimal() +
    theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      axis.title.y = element_blank(),
      legend.position = "none",
      text = element_text(family = "Avenir")
    ) +
    annotate("text", y = highlight$hits + 5, x = highlight$location, label = highlight$hits, color = "#007dc2", size = 5) +
    scale_y_continuous(expand = c(0,0))

  by_regionplot
})



renderPlotly({
  by_regionplot()
})
  
```

```{r}

# renderPlotly({
#    by_region= by_region()
# 
#   # filter data for top 25 locations
#   top_25 <- by_region %>%
#     filter(hits >= 3) %>%
#     head(25)
# 
#   # select the highlighted location
#   highlight <- by_region %>%
#     # filter(hits >= 3) %>%
#     filter(ToHighlight == "yes")
# 
#   # For loop to
#   if(any(top_25$ToHighlight == "yes") == TRUE) {
#     region <- top_25
#   } else{
#     region <- rbind(top_25, highlight)
#   }
# 
#   region %>%
#     ggplot(aes(x = reorder(location, hits), y = hits, fill = ToHighlight )) +
#     geom_col() +
#     coord_flip() +
#     labs(title = paste("Hits by Region for Search Term:", input$keyword1_id),
#          x = "Location",
#          y = "Number of Hits") +
#     scale_fill_manual( values = c( "yes"="#007dc2", "no"="gray" ), guide = FALSE ) +
#     theme_minimal() +
#     theme(
#       panel.background = element_blank(),
#       panel.grid = element_blank(),
#       plot.background = element_blank(),
#       axis.title.y = element_blank(),
#       legend.position = "none",
#       text = element_text(family = "Avenir")
#     ) +
#     annotate("text", y = highlight$hits + 5, x = highlight$location, label = highlight$hits, color = "#007dc2", size = 5) +
#     scale_y_continuous(expand = c(0,0))
# })

  
```

Hits Per Capita Per Region
-----------------------------------------------------------------------

### Hits Per Capita By Region

```{r}
by_region_popplot <- eventReactive(input$goButton, {
  
  by_region_pop = by_region_pop()
  
  # filter data for top 25 locations
  top_25 <- by_region_pop %>% 
    head(25)
  
  # select the highlighted location
  highlight <- by_region_pop %>% 
    filter(ToHighlight == "yes")
  
  # For loop to 
  if(any(top_25$ToHighlight == "yes") == TRUE) {
    region_pop <- top_25
  } else{
    region_pop <- rbind(top_25, highlight)
  }
  
  by_region_popplot <- region_pop %>% 
    filter(hitspercapita >= 0) %>% 
    ggplot(aes(x = reorder(location, hitspercapita), y = hitspercapita, fill = ToHighlight )) +
    geom_col() + 
    coord_flip() + 
    labs(title = paste("Hits Per Capita by Region for Search Term:", input$keyword1_id),
                                     x = "Location",
                                     y = "Number of Hits Per Capita") +
    scale_fill_manual( values = c( "yes"="#007dc2", "no"="gray" ), guide = FALSE ) +
    theme_minimal() +
    theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      axis.title.y = element_blank(),
      text = element_text(family = "Avenir"),
      legend.position = "none",
    ) +
    annotate("text", y = highlight$hitspercapita, x = highlight$location, label = round(highlight$hitspercapita, 6), color = "#007dc2", size = 4, family = "Avenir", vjust = -.05) +
    scale_y_continuous(expand = c(0,0))
  
  by_region_popplot
  
})

renderPlotly({
  by_region_popplot()
})
  
```

```{r}
# renderPlotly({
#   by_region_pop = by_region_pop()
#   
#   # filter data for top 25 locations
#   top_25 <- by_region_pop %>% 
#     head(25)
#   
#   # select the highlighted location
#   highlight <- by_region_pop %>% 
#     filter(ToHighlight == "yes")
#   
#   # For loop to 
#   if(any(top_25$ToHighlight == "yes") == TRUE) {
#     region_pop <- top_25
#   } else{
#     region_pop <- rbind(top_25, highlight)
#   }
#   
#   region_pop %>% 
#     filter(hitspercapita >= 0) %>% 
#     ggplot(aes(x = reorder(location, hitspercapita), y = hitspercapita, fill = ToHighlight )) +
#     geom_col() + 
#     coord_flip() + 
#     labs(title = paste("Hits Per Capita by Region for Search Term:", input$keyword1_id),
#                                      x = "Location",
#                                      y = "Number of Hits Per Capita") +
#     scale_fill_manual( values = c( "yes"="#007dc2", "no"="gray" ), guide = FALSE ) +
#     theme_minimal() +
#     theme(
#       panel.background = element_blank(),
#       panel.grid = element_blank(),
#       plot.background = element_blank(),
#       axis.title.y = element_blank(),
#       text = element_text(family = "Avenir"),
#       legend.position = "none",
#     ) +
#     annotate("text", y = highlight$hitspercapita, x = highlight$location, label = round(highlight$hitspercapita, 6), color = "#007dc2", size = 4, family = "Avenir", vjust = -.05) +
#     scale_y_continuous(expand = c(0,0))
# })
  
```

Interest Over Time Comparison
-----------------------------------------------------------------------

### Interest Over Time

```{r}
int_timeplot <- eventReactive(input$goButton, {
  int_over_time = int_over_time()
  
  int_timeplot <- int_over_time %>% 
    ggplot(aes(x = date, y = hits)) +
    geom_line(aes(color = Region), size = 0.5) +
    labs(title = paste("US Search Volume Over Time for Search Term:", input$keyword1_id),
                                     x = "Date",
                                     y = "Hits") + 
    scale_color_manual(values = c("#e08f5b", "#007dc2")) +
    theme_minimal() +
    theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      axis.title.x = element_blank(),
      text = element_text(family = "Avenir")
    )
  
  int_timeplot
})

renderPlotly({
  int_timeplot()
  
})

```

```{r}

# renderPlotly({
#   int_over_time = int_over_time()
#   
#   int_over_time %>% 
#     ggplot(aes(x = date, y = hits)) +
#     geom_line(aes(color = Region), size = 0.5) +
#     labs(title = paste("US Search Volume Over Time for Search Term:", input$keyword1_id),
#                                      x = "Date",
#                                      y = "Hits") + 
#     scale_color_manual(values = c("#e08f5b", "#007dc2")) +
#     theme_minimal() +
#     theme(
#       panel.background = element_blank(),
#       panel.grid = element_blank(),
#       plot.background = element_blank(),
#       axis.title.x = element_blank(),
#       text = element_text(family = "Avenir")
#     )
#   
# })

```

Streamgraph example
-----------------------------------------------------------------------

### Streamgraph

```{r}

int_stream <- eventReactive(input$goButton,{
  int_over_time = int_over_time()
    
  # Different Version
  int_stream <- int_over_time %>%
    streamgraph(key="Region", value="hits", date="date") %>%
    sg_axis_x(5, "year", "%Y") %>%
    sg_axis_y(0) %>%
    sg_fill_manual(values = c("#e08f5b", "#007dc2"))
  
  int_stream
})

renderStreamgraph({
  int_stream()
})

```

```{r}
# renderStreamgraph({
#   int_over_time = int_over_time()
# 
#   # int_over_time %>% 
#   #   ggplot(aes(x = date, y = hits)) +
#   #   geom_line(aes(color = Region), size = 0.5) +
#   #   labs(title = paste("US Search Volume Over Time for Search Term:", input$keyword1_id),
#   #                                    x = "Date",
#   #                                    y = "Hits") + 
#   #   scale_color_manual(values = c("#e08f5b", "#007dc2")) +
#   #   theme_minimal() +
#   #   theme(
#   #     panel.background = element_blank(),
#   #     panel.grid = element_blank(),
#   #     plot.background = element_blank(),
#   #     axis.title.x = element_blank(),
#   #     text = element_text(family = "Avenir")
#   #   )
#   
#   # int_over_time %>%
#   #   streamgraph(key="Region", value="hits", date="date", offset = "silhouette", interpolate = "step") %>% 
#   #   sg_axis_x(5, "year", "%Y") %>% 
#   #   sg_axis_y(0) %>%
#   #   sg_fill_manual(values = c("#e08f5b", "#007dc2"))
#     
#   # Different Version
#   int_over_time %>%
#     streamgraph(key="Region", value="hits", date="date") %>%
#     sg_axis_x(5, "year", "%Y") %>%
#     sg_axis_y(0) %>%
#     sg_fill_manual(values = c("#e08f5b", "#007dc2"))
# 
# })

```

Topic Graph
--------------------------------------------------------------------

### Topic Graph

```{r}

renderPlot({
  topqueries = topqueries()
  
  topqueries_bigram <- topqueries %>% 
    count(word1, word2, word3, sort = TRUE) %>% 
    filter(!is.na(word1), !is.na(word2), !is.na(word3)) %>% 
    graph_from_data_frame() 
  
  # arrow for graph
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

  # Set Seed
  set.seed(42)

  # Graph related top queries
  ggraph(topqueries_bigram, layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                   arrow = a, end_cap = circle(.07, 'inches'), edge_colour = "#007dc2") +
    geom_node_point(color = "#003769", size = 3) +
    geom_node_text(aes(label = name), 
                   vjust = 1, hjust = 1,
                   repel = TRUE, 
                   point.padding = unit(0.2, "lines")) +
    theme_void() +
    labs(title = "Google Trends: top queries (US)",
         caption = "source: @eeysirhc") +
    theme(
      panel.background = element_blank(),
      panel.grid = element_blank(),
      plot.background = element_blank(),
      text = element_text(family = "Avenir")
    )
})

```

Rising Queries
--------------------------------------------------------------------

### Rising Queries

```{r}

renderPlot({
  risingqueries = risingqueries()
  
  US <- gtrends(keyword = input$keyword1_id,
        geo = "US",  #default always US 
        time = input$time_id)
  
  US_related <- as_tibble(US$related_queries)
  
  
  word_counts <- US_related %>% 
    select(value) %>% 
    unnest_tokens(word, value) %>% 
    count(word, sort = TRUE) %>% 
    filter(!word %in% stop_words$word)
  
  risingqueries_bigram <- risingqueries %>% 
    count(word1, word2, word3, sort = TRUE) %>% 
    filter(!is.na(word1), !is.na(word2), !is.na(word3)) %>% 
    graph_from_data_frame(vertices = word_counts)
  
  a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

  set.seed(42)

  ggraph(risingqueries_bigram, layout = "fr") +
    geom_edge_link(aes(edge_alpha = n), 
                   show.legend = FALSE,
                   arrow = a, 
                   end_cap = circle(.07, 'inches'), 
                   edge_colour = "#007dc2") +
    geom_node_point(aes(size = n, color = n)) +
    geom_node_text(aes(label = name), 
                   vjust = 1, hjust = 1,
                   repel = TRUE, 
                   point.padding = unit(0.2, "lines")) +
    scale_color_gradient2(low = '#e08f5b', high = '#8cc5be', midpoint = 25) +
    theme_void() +
    theme(
      legend.position = 'none',
      text = element_text(family = "Avenir")
    ) +
    labs(title = 'Google Trends: rising queries (US)',
         caption = "source: @eeysirhc") 

})
```


Data Output
=====================================================================

Row
--------------------------------------------------------------------

### Hits by Region Data

```{r}
DT::renderDataTable({
  by_region = by_region()
  
  DT::datatable(
    by_region, 
    options = list(bPaginate = TRUE)
  )
})


# Download Button
downloadButton("table1", label = "Download Hits By Region")

downloadHandler(
  filename = function() {
    "output/hits_region.csv"
  },
  content = function(file) {
    write.csv(by_region(), file)
  }
)
  
```


Row
--------------------------------------------------------------------

### Hits by Region per Capita Data

```{r}
DT::renderDataTable({
  by_region_pop = by_region_pop()
  
  by_region_pop$hitspercapita <- round(by_region_pop$hitspercapita, 7)
    
  
  DT::datatable(
    by_region_pop, 
    options = list(bPaginate = TRUE)
  )
})


# Download Button
downloadButton("table2", label = "Download Hits per Capita")

downloadHandler(
  filename = function() {
    "output/hits_capita.csv"
  },
  content = function(file) {
    write.csv(by_region_pop(), file)
  }
)

```

Row
--------------------------------------------------------------------

### Interest Over Time Data

```{r}
DT::renderDataTable({
  int_over_time = int_over_time()
  
  DT::datatable(
    int_over_time, 
    options = list(bPaginate = TRUE)
  )
})


# Download Button
downloadButton("table2", label = "Download Interest Over Time")

downloadHandler(
  filename = function() {
    "output/int_over_time.csv"
  },
  content = function(file) {
    write.csv(int_over_time(), file)
  }
)

```

Row
--------------------------------------------------------------------

### Top Queries Data

```{r}
DT::renderDataTable({
  topqueries = topqueries()
  
  DT::datatable(
    topqueries, 
    options = list(bPaginate = TRUE)
  )
})


# Download Button
downloadButton("table3", label = "Download Top Queries")

downloadHandler(
  filename = function() {
    "output/top_queries.csv"
  },
  content = function(file) {
    write.csv(topqueries(), file)
  }
)
```

Row
--------------------------------------------------------------------

### Rising Queries Data

```{r}
DT::renderDataTable({
  risingqueries = risingqueries()
  
  DT::datatable(
    risingqueries, 
    options = list(bPaginate = TRUE)
  )
})


# Download Button
downloadButton("table4", label = "Download Rising Queires")

downloadHandler(
  filename = function() {
    "output/rising_queries.csv"
  },
  content = function(file) {
    write.csv(risingqueries(), file)
  }
)
```

Batch Processing
=====================================================================

Inputs {data-height=100}
---------------------------------------------------------------------

```{r inputs_new}

# Select Keyword
textInput(
  inputId = "keyword1_id",
  label = "Select Keyword",
  value = "Sustainable"
)

textInput(
  inputId = "keyword2_id",
  label = "Select Keyword",
  value = "Sustainable"
)

textInput(
  inputId = "keyword3_id",
  label = "Select Keyword",
  value = "Sustainable"
)

# add apply button so the graph doesn't refresh automatically
# applyButton()

```

Row {data-height=50}
--------------------------------------------------------------------

__Coming Soon__: This will eventually batch process different keywords and save them into individual files in an output folder. 

Row
--------------------------------------------------------------------

### Output

```{r}

search_terms <- reactive({
  search_terms <- as.vector(c(input$keyword1_id, input$keyword2_id, input$keyword3_id))
  search_terms
})

```

